\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2021-07-23 manuscript.tex
Update package versions

\begin{Schunk}
\begin{Sinput}
> tmat <- rbind(
+   c(NA, 1, 2),
+   c(NA, NA, 3),
+   c(NA, NA, NA)
+ )
> colnames(tmat) <- rownames(tmat) <- c("Stable", "Progression", "Dead")
> tmat
\end{Sinput}
\begin{Soutput}
            Stable Progression Dead
Stable          NA           1    2
Progression     NA          NA    3
Dead            NA          NA   NA
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> library("hesim")
> library("data.table")
> n_patients <- 1000
> patients <- data.table(
+   patient_id = 1:n_patients,
+   age = rnorm(n_patients, mean = 45, sd = 7),
+   female = rbinom(n_patients, size = 1, prob = .51)
+ )
> 
> states <- data.table(
+   state_id = c(1, 2),
+   state_name = c("Stable", "Progression") 
+ )
> 
> strategies <- data.table(
+   strategy_id = 1:3,
+   strategy_name = c("SOC", "New 1", "New 2"),
+   soc = c(1, 0, 0),
+   new1 = c(0, 1, 0),
+   new2 = c(0, 0, 1)
+ )
> 
> hesim_dat <- hesim_data(
+   strategies = strategies,
+   patients = patients,
+   states = states
+ )
> hesim_dat
\end{Sinput}
\begin{Soutput}
$strategies
   strategy_id strategy_name soc new1 new2
1:           1           SOC   1    0    0
2:           2         New 1   0    1    0
3:           3         New 2   0    0    1

@@

\begin{Schunk}
\begin{Sinput}
> labs_indiv <- get_labels(hesim_dat)
> labs_indiv
\end{Sinput}
\begin{Soutput}
$strategy_id
  SOC New 1 New 2 
    1     2     3

@@

\begin{Schunk}
\begin{Sinput}
> utility_tbl <- stateval_tbl(
+   data.table(state_id = states$state_id,
+              mean = c(.8, .6),
+              se = c(0.02, .05)
+   ),
+   dist = "beta")
> utility_tbl
\end{Sinput}
\begin{Soutput}
   state_id mean   se
1:        1  0.8 0.02
2:        2  0.6 0.05
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> medcost_tbl <- stateval_tbl(
+   data.table(state_id = states$state_id,
+              mean = c(2000, 9500),
+              se = c(2000, 9500)
+   ),
+   dist = "gamma")
> medcost_tbl
\end{Sinput}
\begin{Soutput}
   state_id mean   se
1:        1 2000 2000
2:        2 9500 9500
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> drugcost_tbl <- stateval_tbl(
+   drugcost_dt,
+   dist = "fixed")
> drugcost_tbl
\end{Sinput}
\begin{Soutput}
    strategy_id state_id time_id time_start time_stop   est
 1:           1        1       1       0.00      0.25  2000
 2:           1        1       2       0.25       Inf  2000
 3:           1        2       1       0.00      0.25  1500
 4:           1        2       2       0.25       Inf  1200
 5:           2        1       1       0.00      0.25 12000
 6:           2        1       2       0.25       Inf 12000
 7:           2        2       1       0.00      0.25  1500
 8:           2        2       2       0.25       Inf  1200
 9:           3        1       1       0.00      0.25 15000
10:           3        1       2       0.25       Inf 15000
11:           3        2       1       0.00      0.25  1500
12:           3        2       2       0.25       Inf  1200
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> drugcost_tbl <- stateval_tbl(
+   drugcost_dt[time_start ==  0][, time_start := NULL],
+   dist = "fixed")
> drugcost_tbl
\end{Sinput}
\begin{Soutput}
   strategy_id state_id   est
1:           1        1  2000
2:           1        2  1500
3:           2        1 12000
4:           2        2  1500
5:           3        1 15000
6:           3        2  1500
\end{Soutput}
\end{Schunk}

>>>>

\begin{Schunk}
\begin{Sinput}
R> tmat <- rbind(
+    c(NA, 1, 2),
+    c(NA, NA, 3),
+    c(NA, NA, NA)
+  )
R> colnames(tmat) <- rownames(tmat) <- c("Stable", "Progression", "Dead")
R> tmat
\end{Sinput}
\begin{Soutput}
            Stable Progression Dead
Stable          NA           1    2
Progression     NA          NA    3
Dead            NA          NA   NA
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> library("hesim")
R> library("data.table")
R> n_patients <- 1000
R> patients <- data.table(
+    patient_id = 1:n_patients,
+    age = rnorm(n_patients, mean = 45, sd = 7),
+    female = rbinom(n_patients, size = 1, prob = .51)
+  )
R> 
R> states <- data.table(
+    state_id = c(1, 2),
+    state_name = c("Stable", "Progression") 
+  )
R> 
R> strategies <- data.table(
+    strategy_id = 1:3,
+    strategy_name = c("SOC", "New 1", "New 2"),
+    soc = c(1, 0, 0),
+    new1 = c(0, 1, 0),
+    new2 = c(0, 0, 1)
+  )
R> 
R> hesim_dat <- hesim_data(
+    strategies = strategies,
+    patients = patients,
+    states = states
+  )
R> hesim_dat
\end{Sinput}
\begin{Soutput}
$strategies
   strategy_id strategy_name soc new1 new2
1:           1           SOC   1    0    0
2:           2         New 1   0    1    0
3:           3         New 2   0    0    1

@@

\begin{Schunk}
\begin{Sinput}
R> labs_indiv <- get_labels(hesim_dat)
R> labs_indiv
\end{Sinput}
\begin{Soutput}
$strategy_id
  SOC New 1 New 2 
    1     2     3

@@

\begin{Schunk}
\begin{Sinput}
R> utility_tbl <- stateval_tbl(
+    data.table(state_id = states$state_id,
+               mean = c(.8, .6),
+               se = c(0.02, .05)
+    ),
+    dist = "beta")
R> utility_tbl
\end{Sinput}
\begin{Soutput}
   state_id mean   se
1:        1  0.8 0.02
2:        2  0.6 0.05
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> medcost_tbl <- stateval_tbl(
+    data.table(state_id = states$state_id,
+               mean = c(2000, 9500),
+               se = c(2000, 9500)
+    ),
+    dist = "gamma")
R> medcost_tbl
\end{Sinput}
\begin{Soutput}
   state_id mean   se
1:        1 2000 2000
2:        2 9500 9500
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> drugcost_tbl <- stateval_tbl(
+    drugcost_dt,
+    dist = "fixed")
R> drugcost_tbl
\end{Sinput}
\begin{Soutput}
    strategy_id state_id time_id time_start time_stop   est
 1:           1        1       1       0.00      0.25  2000
 2:           1        1       2       0.25       Inf  2000
 3:           1        2       1       0.00      0.25  1500
 4:           1        2       2       0.25       Inf  1200
 5:           2        1       1       0.00      0.25 12000
 6:           2        1       2       0.25       Inf 12000
 7:           2        2       1       0.00      0.25  1500
 8:           2        2       2       0.25       Inf  1200
 9:           3        1       1       0.00      0.25 15000
10:           3        1       2       0.25       Inf 15000
11:           3        2       1       0.00      0.25  1500
12:           3        2       2       0.25       Inf  1200
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> drugcost_tbl <- stateval_tbl(
+    drugcost_dt[time_start ==  0][, time_start := NULL],
+    dist = "fixed")
R> drugcost_tbl
\end{Sinput}
\begin{Soutput}
   strategy_id state_id   est
1:           1        1  2000
2:           1        2  1500
3:           2        1 12000
4:           2        2  1500
5:           3        1 15000
6:           3        2  1500
\end{Soutput}
\end{Schunk}
